\documentclass[line]{res}
\usepackage{multicol}
\setlength{\columnsep}{1cm}
\newsectionwidth{0cm}

\begin{document}
\name{Ryan Serazin}
\address{8126 Lakeshore Rd, Burtchville, MI, 48059}
\address{(810) 304 - 6041 \\ rps9530@rit.edu \\ github.com/esapyr}

\begin{resume}
\begin{multicols}{2}

\section{Personal Projects}
\begin{itemize}
    \item Wrote an interpreter for McCarthy's original lisp in rust
    \item Wrote an asynchronous graphical client server chat application in clojure using the aleph library
    \item Hacked on a django application during rit48 that connected students looking to build a team for a personal project. 
    \item Hacked on a flask app to help manage team and point information for an annual penny wars philanthropic event.
    \item Hacked on a clojure app to help manage service hour reporting.
\end{itemize}

\section{Education}
B.S. of Computer Science expected in 2016 with a minor in philosophy 
\\
\textbf{Relevant Courses}: Data Mining, Functional Programming Skills, Software Engineering, Artificial Intelligence, 
Programming Language Concepts, Professional Communication, Concepts of Computer Systems, Operating Systems, 
Computer Science Theory, Data Communication, Analysis of Algorithms, Parallel and Distributed Systems.

\section{Skills}
\begin{itemize}
    \item \textbf{Languages:} Clojure, Haskell, Rust, Python, Java, Javascript, HTML/CSS, PHP, C/C++
    \item \textbf{Libraries:} Ring/Compojure, Flask, Django, Angular, Nodejs, D3
    \item \textbf{Text Editors:} Vim, Eclipse, Lighttable, Visual Studio
    \item \textbf{Operating Systems:} GNU/Linux, Windows 8/7, OS X
    \item \textbf{Source Control:} git
\end{itemize}

\columnbreak

\section{Internships \& Co-ops}
\textit{Showcase IDX, Remote \hfill{2014-2015 School Year}}
\begin{itemize}
    \item Currently writing an administrator interface in Clojure to allow customers and resellers to better 
          manage their service, as well as to help the support team when onboarding and providing support.
\end{itemize}

\textit{Tourbuzz, Atlanta GA \hfill{Summer 2014}}
\begin{itemize}
    \item Wrote a PHP app that routed incoming support calls to the highest priority support member available,
          while also finding the incoming caller's information and sending it to the support member over hipchat.
    \item Wrote Clojure app that translated Dieselpoint queries into Elasticsearch queries on the the fly 
          using a hand writen context free grammar.
    \item Architected a Javascript app that used Angular and D3 to find trends in customer information over time.
\end{itemize}

\textit{National Technical Institue for the Deaf, Rochester NY \hfill{Summer 2013}}
\begin{itemize}
    \item Wrote and compiled a very limited graphical front end for editing video with FFMPEG using Tkinter in Python.
    \item Maintained a course management system written in Javascript and ASP classic.
\end{itemize}

\textit{Maclean-Fogg, Royal Oak MI \hfill{Summer 2012}}
\begin{itemize}
    \item Designed and implemented an ASP.net website and backing database for all maintenance 
          department staff at Maclean-Fogg's facilities to track part usage.
    \item Wrote a small C\# script that organized internal documentation that had been recently been digitized for our 
          paperless information system.
    \item Wrote a VBA macro for outlook that extracted tooling shortage messages sent by the ERP system and 
          entered them into a database.
\end{itemize}
\end{multicols}
\end{resume}
\end{document}
